This section categorizes previously proposed incentivization schemes into three
groups.

\noindent \emph{1. Non-transferable benefits:} these proposals aim to recruit
relays by offering some privileged status intended for personal use which cannot
be \emph{securely} sold for reimbursement of financial
investment~\cite{dingledine2010building,jansen2010recruiting, jansen2013lira}.
	  
\noindent \emph{2. Transferable benefits:} these schemes offer privileged
service or products intended to hold value on a secondary resale market. These
indirect financial incentives presume to attract a broader demand than in the
non-transferable case. Partial proof-of-work tokens that can then be redeemed by
relays for profit in real cryptocurrency mining pools~\cite{biryukov2015proof}
and exchangeable shallots in TEARS~\cite{jansen2014onions} are part of this
category.

\noindent \emph{3. Monetary payments:} these schemes offer rewards with what
might be considered real money that holds external value.
PAR~\cite{androulaki2008payment} allows clients to send direct payments to
relays in a hybrid payment scheme which makes use of inefficient but anonymous
Chaumian e-cash protocols~\cite{chaum1988untraceable} and efficient but
transparent probabilistic micropayments. PAR introduces the \emph{honest but
  curious} bank paradigm in which the bank cannot deanonymize clients but is in
control of their deposited financial assets. PAR suffers from scalability issues
owing to its strongly centralized architecture. Other monetary payments schemes
such as Xpay~\cite{chen2009xpay} and the proposal of Carbunar~\textit{et
  al.}~\cite{carbunar2012tipping} are limited by the same \emph{honest but
  curious} security assumptions and their scalability remains capped by the need
for all clients to interact with the central bank for each payment chain. The
moneTor scheme can be seen as a member of this family of solutions, with the
following advances: moneTor removes the need to rely on a \textit{honest but
  curious} bank, and offers a solution to the scalability issue inherent to
previous approaches.


%\footnote{Generally speaking, incentives provided by monetary payments
%  are more economically robust than transferable benefits, which in turn are
%  more robust than non-transferable benefits. Although we examine related works
%  through the prism of economic appeal, this is not a statement of superiority
%  so much as an observation on diverging motivation. Indeed, a number of
%  sociological and legal implications must be weighed before
%  introducing financial profitability into the Tor ecosystem. We consider these
%  to be out of scope for the purposes of our research.}

%\op{Need to explain why our solution is better/more interesting than all these.}

%\paragraph*{Non-transferable benefits - Gold Star} As one of the earliest
%incentive proposals, Gold Star introduces the notion of premium bandwidth.
%Premium, or \emph{gold star} status, is awarded exclusively to the fastest 7/8
%fraction of relays, signalling to the rest of the network that these relays can
%enjoy prioritized traffic. While highly attractive for its conceptual
%simplicity, Gold Star leaks a considerable amount of user information since
%priortized traffic can now be trivially attributed to this relatively small set
%of gold star relays~\cite{dingledine2010building}, since gold star is by design
%non-transferable.

By leveraging recent advances in cryptocurrency, our scheme offers
straightforward improvements to prior similar works in the last category,
primarily by reducing trust and improving scalability. In contrast, the
trade-offs with state-of-the-art solutions in the first two categories is more
nuanced. We will highlight some select considerations here.

\paragraph*{Non-transferable benefits - BRAIDS/LIRA} The BRAIDS scheme
introduces \emph{tickets} to represent premium status. Users may wish to
transfer tickets to other users, but this transfer must be done through a
trusted-third party. Small numbers of ephemeral tickets are freely distributed
by a central \emph{bank} to any client upon request or to relays that have
accumulated tickets spent by clients. Crucially, tickets can only be spent at a
single relay defined at the time of their minting, in order to circumvent the
double spending problem~\cite{jansen2010recruiting}. However, users may exchange
accumulated tickets for tickets from other relays through a central bank within
a set time interval. BRAIDS raises four major concerns: 1)~everyone connects to
a central bank through Tor, which raises scalability issues; 2) the bank is not
trustless: by design the bank can issue valid tickets for anyone, and guard
relays can steal tickets in the distribution process; 3) verifying a blind
signature on relay side for each payment is computationally intensive if the
rate of payment is high, and current high-bandwidth Tor relays are already
CPU-bound; 4) the fact that tickets are relay-specific means that users must
interact frequently with the bank. Consequently, users have two costly options
as the network increases: stockpile a large number of tickets for each relay or
interact frequently with the central bank.

LIRA is an ideological successor to BRAIDS which reduces scalability issues and
improves the efficiency of the relay side verification of tickets by a factor
$\approx 80$. Clients in LIRA probabilistically ``win'' premium tickets without
any interaction with the bank. While LIRA improves the efficiency of BRAIDS, and
could even offer high fairness (by supporting high payment rates), it suffers
from a \textit{client} cheating incentive to continuously build circuits to try
to win premium tickets~\cite{jansen2013lira, jansenblogpost}. Depending on the
chosen value for the payment rate, this problem alone could prevent the scheme
from offering a realistic option. If the payment rate is too low, then the
incentive to cheat increases as a the scheme awards a large priority bandwidth
between guesses to the cheater. If the payment rate is too high, then guessers
would have difficulties maintaining good guesses through their circuit lifetime
since the probability of maintaining winning guesses exponentially decreases
with payment rate. As a result, LIRA's goal of increasing buyer anonymity
through successful guessers loses its efficacy. Moreover, LIRA does not
address Concerns 2) and 4) inherited from BRAIDS.

Compared to BRAIDS and LIRA, moneTor offers the ability to prevent
double-spending without suffering from a centralized exchange process
(BRAIDS)~\cite{jansenblogpost}, or from incentives to cheat to gain premium
access and stockpile relay-specific information (LIRA). Moreover, moneTor offers
high fairness with on-the-fly payment verification improved by a factor $\approx
6$ compared to LIRA (one $\hash$ operation instead of six $\hash$ + a few XORs
and multiplications) and $\approx 500$ to BRAIDS. This does not account for
opening and closing the nanopayment channel, happening outside of the data
transfer time window and for which the relay's costly operation is to perform
one ZKP (opening) and generating one blind signature (closing). Also, moneTor
does not suffer from concern 2) and moneTor tokens can act as a wrapper from an
external cryptocurrency such as Bitcoin or Ethereum using inter-ledger
protocols~\cite{back2014enabling, poon2017plasma}.
%  \op{Do you mean that we need to be stuck to an
%  existing crypto-currency if we want problem 2) to be solved? I do
%  not see why, and this looks bad -- many people are likely to not
%  want to be linked to an external currency.} 
  Finally and more important, moneTor tokens are not relay-specific, which
  solves the scalability problem on the economic appeal (i.e., in moneTor,
  frozen funds are independent of the network size).
%Finally, moneTor payments offer to the relays what we could consider real
%money, that can be transferred or used to buy premium bandwidth directly (while
%in LIRA and BRAIDS, an exchange process with the bank is needed).

\paragraph*{Transferable benefits - TEARS} TEARS introduces a two-layer approach
whereby \emph{shallots} token are awarded by a distributed semi-trusted bank to
participating relays. These shallots, which are securely exchanged tokens, can
then be redeemed for BRAIDS-style \emph{Priority Passes}. While fully
exchangeable shallots represent an economic improvement over non-transferable
privileges, these tokens are conceptually discrete and indivisible assets that
are not as easily exchanged as true currency. We expect our ecosystem to be more
user friendly, offering arbitrarily high transferability and divisibility of
priority tokens without changing the underlying Tor architecture, while also
scaling on trustless entities (our intermediaries) instead of a distribution of
semi-trusted banks that must be operated by reputable parties. The moneTor
scheme is also designed for fair-exchange with Bolt's ZKP construction to open
and close the nanopayment channels but offering $n$ nanopayments for which the
relay only has to perform $1$ $\hash$ operation to validate. This is a strong
contrast to TEARS, which requires a blind signature for each payment. We also
expect the fair-exchange property to be of critical importance to enable
short-bandwidth and short-lived premium Tor circuits, which were the majority
among observed active circuits of our measurement study. Finally, a major
difference with previous work (TEARS, LIRA, BRAIDS) is that moneTor does not
depend on a relay's bandwidth audit to distribute tokens. Relays receive
currency directly from client from the rate of provided bandwidth and
potentially more from the Tor authorities after tax redistribution. Although the
tax redistribution phase will require bandwidth audits, the importance of this
step is a tunable function of the tax rate itself. Note, however, that direct
payments do introduce a separate mode of abuse. In principle, exit relay in
moneTor have an incentive to inflate network traffic by injecting junk traffic
(e.g. padding cells) or even conspiring with the destination server to send
useless data to the client. We would propose to mitigate this risk by
implementing junk traffic monitoring into the existing measurement
infrastructure by running premium and non-premium circuits through measured
relays. Currently junk traffic produced by the exit node is already a severe
issue~\cite{rochet2018dropping} that has prompted the release of several patches
by the Tor project. However, the conspirator problem appears to be intractable
by nature since the junk data would appear legitimate to the Tor circuit layer.
As a coarse-grain mitigation strategy, we can cap the number of nanopayments
available to each circuit. A conspirator can then be reduced to non-fair
exchange problem, which is what previous works offer as a basis. Moreover,
websites might not be incentivized to coerce and insert junk traffic, given the
impact it could produce on the website rendering, and to its reactivity to user
events.



%Furthermore, its reliance on a centralized bank and bandwidth
%measurement authority place implicit limits on its scalability and
%security~\cite{jansen2010recruiting}.

%\paragraph*{TorPath to TorCoin} TorCoin proposes to revamp the Tor
%architecture into one which can serve as the basis for a new cryptocurrency
%mined via a method called proof-of-bandwidth. The networking component specifies
%verifiable pseudorandom shuffling as the new method for user circuit
%selection. This modified protocol would in theory provide a weakly secure means
%for relays to mint new TorCoin tokens based on their bandwidth
%contribution~\cite{ghosh2014torpath}. Although the research is an ambitious
%attempt to simultaneously tackle many challenges including both the bandwidth
%measurement and relay incentivization problems, the authors are clear in stating
%that many questions remain regarding the security and feasibility of the scheme,
%which would in effect require a network-wide overhaul of the design of Tor.
%%While researching on TorCoin-like approach has the potential to help the Tor
%%project on one of the fundamental security problems (i.e., the bandwidth
%%measurement system), outcomes are not clear as many vulnerabilities and
%%deployment questions remain.

%\paragraph*{Transferable benefits - Proof-of-work as anonymous micropayment} Users in this simple design
%provide partial proof-of-work tokens that can then be redeemed by relays for
%profit in real cryptocurrency mining pools. The drawback of this scheme is
%simply an issue of unrealistic magnitude; the paper estimates that a user who
%continuously mines with typical consumer CPU hardware will be able to make only
%a few cents worth of payments every 24 hours while incurring a much higher cost
%in electricity~\cite{biryukov2015proof}.

%\paragraph*{Monetary Payment - PAR} A pre-Bitcoin design, PAR~\cite{androulaki2008payment}
%allows clients to send direct payments to relays in a hybrid payment scheme
%which makes use of inefficient but anonymous Chaumian e-cash
%protocols~\cite{chaum1988untraceable} and efficient but transparent
%probabilistic micropayments. PAR introduces the \emph{honest but curious} bank
%paradigm in which the bank cannot deanonymize clients but is in control of their
%deposited financial assets. As with BRAIDS, PAR suffers from an unscalable
%design owing to its centralized architecture.
%
%\paragraph*{Monetary Payment - ORPay, PlusPay, CoinPay} These three protocols, part of the
%Chaumian e-cash tradition of payments schemes, are a series of incremental
%improvements released across Xpay~\cite{chen2009xpay} and Carbunar~\textit{et al.}~\cite{carbunar2012tipping}.
% In each of the designs, the micropayment building block
%is derived from Payword hash chains~\cite{rivest1996payword}, as is ours. While
%the schemes offer practical advantages to many aspects of PAR, they are limited
%by the same \emph{honest but curious} security assumptions and their scalability
%remains capped by the need for all clients to interact with the central bank for
%each payment chain. The moneTor scheme can be seen as an idealogical member of
%this family of solutions. In the remainder of the paper, we will explain how our
%payment channel approach resolves the scalability problems inherent in the
%existing protocols and explore the auxillary implications in greater detail than
%in prior works.

%\subsubsection{Orchid} Orchid is an alternative project to Tor altogether which we
%include for thoroughness and some broad ideological similarities
%~\cite{salamon2018orchid}. It is an Ethereum-based project proposing to
%construct a brand new decentralized and market-based anonymous routing
%network. However, its stated intent focuses on censorship resistance rather
%than strong anonymity and therefore lacks comparable privacy guarantees with
%Tor. Indeed, the external payment protocol adopted by Orchid makes no claims on
%anonymity whatsoever~\cite{pass2015micropayments}.


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../popets_monetor"
%%% End:
