\documentclass[sigconf, anonymous]{acmart}

\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage[noend]{algpseudocode}
\algrenewcommand{\algorithmiccomment}[1]{{\color{gray}$\triangleright$ #1}}

\fancyhf{} % Remove fancy page headers
\fancyhead[C]{Anonymous submission \#9999 to ACM CCS 2018} % TODO: replace 9999 with your paper number
\fancyfoot[C]{\thepage}

\setcopyright{none} % No copyright notice required for submissions
\acmConference[Anonymous Submission to ACM CCS 2018]{ACM Conference on Computer and Communications Security}{Due 19 May 2018}{Toronto, Canada}
\acmYear{2018}

\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions
\usepackage{subcaption}
%%\ccsPaper{9999} % TODO: replace with your paper number once obtained
\newcommand{\flo}[1]{ {\color{red} FR: #1}}
\newcommand{\td}[1]{ {\color{blue} TD: #1}}

\begin{document}
\title{Monetary Tor incentives with efficient nanopayment channels} % TODO: replace with your title

\begin{abstract}

  Although it is the most widely-used secure traffic anonymization network in
  the world, Tor nevertheless suffers from shortcomings in network diversity and
  performance. One strategy to mitigate both problems entails the engineering of
  incentives in order to encourage more nodes to act as network relays. In this
  paper, we present moneTor: the first relay incentivization scheme which
  provides sufficiently secure, efficient, and economically robust payments. Our
  approach is constructed from very recent developments in the cryptocurrency
  domain and is designed to be directly implemented into the existing Tor
  architecture. Using a combination of live network data collection and analysis
  of our simulated design, we show that moneTor is demonstratively feasible,
  offering upwards of [X] improved premium bandwidth for paying clients at only
  a [X] cost in network overhead.

  \td{The following (including this abstract) is some combination of incomplete
    and temporary pre-draft reading material. Comments are marked in blue (like this)}

\end{abstract}

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002978.10002991.10002994</concept_id>
<concept_desc>Security and privacy~Pseudonymity, anonymity and untraceability</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10002978.10003014.10003015</concept_id>
<concept_desc>Security and privacy~Security protocols</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[300]{Security and privacy~Pseudonymity, anonymity and untraceability}
\ccsdesc[300]{Security and privacy~Security protocols}

\keywords{Tor, cryptocurrency, payment channels} % TODO: replace with your keywords

\maketitle

\section{Introduction}
\label{sec:introduction}
\input{sections/introduction.tex}

\section{Background}
\label{sec:background}
\input{sections/background.tex}

\section{Related Work}
\label{sec:related_work}
\input{sections/related-work.tex}

\section{Economic Policy}
\label{sec:tor_incentives}
\input{sections/economic-policy.tex}

\section{moneTor Design}
\label{sec:design}
\input{sections/monetor-design.tex}

\section{Experimental Analysis}
\label{sec:analysis}
\input{sections/analysis.tex}

\section{Limitations and Future Work}
\label{sec:limitations_futurework}
%Prioritization
%Channel managmnt
%Side-channel attacks
%more resource evaluation
\subsection{Prioritization}

We explored prioritization with a small modification of the EWMA scheduler, and by playing with the control-flow windows. We discovered that this problem was unexpectedly difficult. We discovered from our experimentations that the EWMA scheduler may currently performing less than optimally due to the exit bandwidth scarcity (in aggregate), and that using it to prioritize premium users may not always work as expected. We believe that prioritization techniques worth further research dedicated to understand better their overall performance impact.

\subsection{Channels Management}

\subsection{Side-channel attacks}
We assumed that our protocol construction would not give more information to an observer than the single bit needed to differentiate a premium user. However in practice, the protocol may leak information through side-channels, such as the time needed to exchange cells in order to open/close channels. An intermediary, or an exit relay may guess bits about the client's location evaluating the round-trip-times of the multi-rounds protocol. Those sort of side-channels attacks are however easily mitigated once they are discovered. Future work may explore such kind of problem and try to obtain more information than the single bit of differentiation.

\section{Code and Data Reproducibility}
\label{sec:code}

\section{Conclusion}
\label{sec:conclusion}
\bibliographystyle{ACM-Reference-Format}
\bibliography{sections/references}

\appendix

\section{Algorithms}
\label{sec:algorithms}
\input{sections/algorithms.tex}

\end{document}